Measuring the Price of Anarchy in Critical Care Unit Interactions

### 2016-03-30 Reviews/response.tex

``
The work presented in this paper contributes to the growing body of literature
by applying state dependent queueing models in a game theoretical context to CCU
interaction.  In particular this consideration allows for the investigation of
targets imposed by central control [4].  The findings of this work justify and
identify a choice of targets that align the interests of the individual
hospitals with social welfare.
''

\subsection{Reviewer 3}

\begin{quote}
    \begin{textit}
        {I recommend that the authors write a more complete and coherent
        Discussion and/or Conclusion which places their work in the context of
        the critcal care system.  It should relate model limitations to the
        critical care system. The current way that limitations are discussed
        is too technical. A brief discussion of stakeholder feedback would
        also be useful.}
    \end{textit}
\end{quote}

This has been addressed, each technical bullet point is now complemented by a
sentence putting the limitation in the context of critical care. Furthermore a
discussion has been added that describes the feedback and further emphasises the
contribution of the work:

``
Despite these mathematical limitations the work presented here gives a strong
analytical evidence as to the use of policies in a decentralised healthcare
environment.

As discussed above, reducing the decision making of critical care managers to
rational reactions to capacity targets is not without limitations. However, this
quantitative model of behaviour was described as insightful and informative
ABUHB. In practice, stakeholders describe a rule of 80\% capacity. Whilst this
is not only at times impossible it is also not evidence based and in particular
does not take in to account interactions between CCUs. This is a common theme in
practice and the literature which this manuscript aims to address.
''

@@

\begin{quote}
    \begin{textit}
        {
        At the beginning of Section 3.1, the authors claim that if neither CCU
        is able to admit patients, then admission to the CCU is cancelled and
        the patient is admitted to a general ward. In my experience modelling
        CCUs, it is highly unlikely that a critical patient would ever be
        admitted to a general ward.  CCU beds are almost always equipped with
        ventilators and ward beds never. I believe that more likely courses of
        action are:
        \begin{itemize}
         \item Sending the patient to another hospital's CCU.  This would be a CCU
           outside of the model.
         \item ``Bumping" a patient currently in the CCU to a ward bed, to free up
           a bed. This would normally be a patient who was nearly ready to be
           transferred to the ward anyway.
         \item Accommodating the patient in the hospital's post-anesthesia care
           unit (PACU), which sometimes functions as an overflow for the CCU.
        \end{itemize}
        I recommend that the authors consult with their stakeholders and
        correct this comment in their paper, if necessary.  This wouldn't have
        any impact on their model, but it is important to use the correct
        language.
        }
    \end{textit}
\end{quote}

This is a very good point, after discussion with our stakeholders we confirm all
the suggestions made by the reviewer and have modified the text:

``
This model assumes that if the bed occupancy level at both Units exceeds a
predetermined threshold, then the admission to the CCU is cancelled. This
cancellation could correspond, to sending the patient to a completely different
CCU (outside of the model), moving one of the current patients (ready to be
dismieed) in the CCU to another ward and/or using the post-anethesisa care unit
as a temporary overflow measure. This models corresponds to the first of those
possibilities: the patient is lost (from the point of view of this model).
''

### 2016-03-30 Paper/paper.tex
First draft of review complete.

This model assumes that if the bed occupancy level at both Units exceeds a predetermined threshold, then the admission to the CCU is cancelled (in reality this implies that patients will be admitted to a general ward within the hospital).
Recalling Figure \ref{arrivalrateregions} this implies:

@@

\begin{itemize}
    \item The assumptions as to the strategy space of our players is restrictive: a single threshold policy might not be optimal (although it is present in various pieces of literature on optimal control of queueing systems: \cite{naor1969regulation, shone2013comparisons});
    \item This model only assumes the presence of two players however in reality the system has a variety of stakeholders. Multi player systems could be worth considering;
    \item The restriction to pure strategies is influenced by discussions with ABUHB and also does not detract from the results presented thanks to the Theorem and Lemma of Section \ref{queueingandgamemodels}.  However, allowing for mixed strategies could also be of interest.
    \item Patient length of stay is assumed to be dependent on the CCU at which they receive service. A further extension of the work would be to use the service rate from original CCU (prior to diversion). This would require a Markov chain with a higher dimensional state space.
\end{itemize}

Despite these limitations the work presented here gives a strong analytical evidence as to the use of policies in a decentralised healthcare environment.
Further work could involve the investigation of patient survival instead of throughput as utility.
This would be similar to work such as \cite{erkut2008ambulance, knight2012ambulance}.

>>>>

This model assumes that if the bed occupancy level at both Units exceeds a
predetermined threshold, then the admission to the CCU is cancelled. This
cancellation could correspond, to sending the patient to a completely different
CCU (outside of the model), moving one of the current patients (ready to be
dismieed) in the CCU to another ward and/or using the post-anethesisa care unit
as a temporary overflow measure. This models corresponds to the first of those
possibilities: the patient is lost (from the point of view of this model).

Recalling Figure \ref{arrivalrateregions} this implies:

@@

\begin{itemize}
    \item The assumptions as to the strategy space of our players is
        restrictive: a single threshold policy might not be optimal (although it
        is present in various pieces of literature on optimal control of
        queueing systems: \cite{naor1969regulation, shone2013comparisons}).
        Indeed, in reality critical care managers could have far more complex
        boundaries for their heuristic decision making;
    \item This model only assumes the presence of two players however in reality
        the system has a variety of stakeholders. Multi player systems could be
        worth considering. This would reflect health boards/hospitals in a
        concentrated area so that interactions are not just between two
        hospitals but between many.
    \item The restriction to pure strategies is influenced by discussions with
        ABUHB and also does not detract from the results presented thanks to the
        Theorem and Lemma of Section \ref{queueingandgamemodels}.  However,
        allowing for mixed strategies could also be of interest, corresponding
        to decision making that is not constant over time. Managers could
        alternate between a variety of behaviours: at time accepting patient
        despite being busy and at other times not;
    \item Patient length of stay is assumed to be dependent on the CCU at which
        they receive service. A further extension of the work would be to use
        the service rate from original CCU (prior to diversion). This would
        require a Markov chain with a higher dimensional state space. In
        practice this corresponds to patient morbidity corresponding to the
        original CCU.
\end{itemize}

Despite these mathematical limitations the work presented here gives a strong
analytical evidence as to the use of policies in a decentralised healthcare
environment.

As discussed above, reducing the decision making of critical care managers to
rational reactions to capacity targets is not without limitations. However, this
quantitative model of behaviour was described as insightful and informative by
ABUHB. In practice, stakeholders describe a rule of 80\% capacity. Whilst this
is not only at times impossible it is also not evidence based and in particular
does not take in to account interactions between CCUs. This is a common theme in
practice and the literature which this manuscript aims to address.

Finally, congestion and throughput is not the only concern of a healthcare
system. Further work could involve the investigation of patient survival instead
of throughput as utility.  This would be similar to work such as
\cite{erkut2008ambulance, knight2012ambulance}.
